Classical Simulation of Quantum Error Correction in a Fibonacci Anyon Code

### 2015-05-26 fib2.tex
add picture of decoder clustering
remove figure

\documentclass[aps, prl, letterpaper, twocolumn, superscriptaddress, notitlepage, 10pt]{revtex4-1}
\usepackage{times}

@@

\begin{figure*}[th!]
\begin{center}
	{\scriptsize (a)
	\includegraphics[width=0.45\columnwidth]{pair-create.pdf}
	\hskip 4pt
	(b)
	\includegraphics[width=0.45\columnwidth]{syndrome-1.pdf}
	\hskip 4pt
	(c)
	\includegraphics[width=0.45\columnwidth]{syndrome-2.pdf}
	\hskip 4pt
	(d)}
	\includegraphics[width=0.45\columnwidth]{syndrome-2.pdf}
\caption{\stf{polish this a bit} The simulation of noise processes proceeds by a) creating pairs of anyons on neighboring tiles represented by open curves b) joining the curves within a given tile c) measuring the total charge on each tile. \stf{Add another graph that shows how we use syndrome info.}}
\label{f:simex}
\end{center}
\end{figure*}

@@

\stf{Add figure about observables versus states.}

@@

Each round of simulation proceeds in four steps as follows (an example is shown 
in \Fref{f:simex}).

\begin{enumerate}[a)]
\item The noise process is modeled by a sequence of pair-creation events distributed as 
a Poisson process across each edge. Curves are created crossing the relevant edge 
and terminating on the neighboring sites.
\item We first join curves that participate in the same tile in order to, 
\cggb{maybe a couple more lines of detail on this and the next point? perhaps also the previous paragraph?}
\item measure the charge on each tile. Any resulting anyon is left somewhere in the tile.
\item The decoder examines this syndrome and clusters nearby anyons. Each cluster 
is then measured (fused), and the decoder continues to cluster and fuse on larger 
scales until there are no more anyons, or a cluster includes a non-trivial loop on the 
lattice. Since operators with support on such non-trivial clusters will generally perform an 
undetectable error on the encoded state, in this case we abandon the simulation and 
declare failure to error correct.
\end{enumerate}

>>>>

\documentclass[aps, prl, letterpaper, twocolumn, superscriptaddress, notitlepage, 10pt]{revtex4-1}
%\documentclass[aps, prl, letterpaper, twocolumn, superscriptaddress, notitlepage, 10pt]{revtex4}
\usepackage{times}

@@

%\begin{figure*}[th!]
%\begin{center}
%	{\scriptsize (a)
%	\includegraphics[width=0.45\columnwidth]{pair-create.pdf}
%	\hskip 4pt
%	(b)
%	\includegraphics[width=0.45\columnwidth]{syndrome-1.pdf}
%	\hskip 4pt
%	(c)
%	\includegraphics[width=0.45\columnwidth]{syndrome-2.pdf}
%	\hskip 4pt
%	(d)}
%	\includegraphics[width=0.45\columnwidth]{syndrome-2.pdf}
%\caption{\stf{polish this a bit} The simulation of noise processes proceeds by a) creating pairs of anyons on neighboring tiles represented by open curves b) joining the curves within a given tile c) measuring the total charge on each tile. \stf{Add another graph that shows how we use syndrome info.}}
%\label{f:simex}
%\end{center}
%\end{figure*}

@@

%\stf{Add figure about observables versus states.}

@@

\begin{figure}[th!]
\begin{center}
	\includegraphics[width=\columnwidth]{pic-decode.pdf}
\caption{The decoder works by maintaining a set of disjoint clusters (rooted trees).}
\label{f:decode}
\end{center}
\end{figure}

%Each round of simulation proceeds in four steps as follows (an example is shown 
%in \Fref{f:simex}).
%
%\begin{enumerate}[a)]
%\item The noise process is modeled by a sequence of pair-creation events distributed as 
%a Poisson process across each edge. Curves are created crossing the relevant edge 
%and terminating on the neighboring sites.
%\item We first join curves that participate in the same tile in order to, 
%\cggb{maybe a couple more lines of detail on this and the next point? perhaps also the previous paragraph?}
%\item measure the charge on each tile. Any resulting anyon is left somewhere in the tile.
%\item The decoder examines this syndrome and clusters nearby anyons. Each cluster 
%is then measured (fused), and the decoder continues to cluster and fuse on larger 
%scales until there are no more anyons, or a cluster includes a non-trivial loop on the 
%lattice. Since operators with support on such non-trivial clusters will generally perform an 
%undetectable error on the encoded state, in this case we abandon the simulation and 
%declare failure to error correct.
%\end{enumerate}
